\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-11-28 projects/project_5/molecular_dynamics/article/article.tex
energy fluctuation comparison done

We are going to run the simulations for a starting temperature of 300 kelvin,
and vary the time step from $1.0 \times 10^{-16}$ to $1.0 \times 10^{-13}$
seconds.
\subsection{Melting temperature of system}
\label{sub:melting_temperature_of_system}

>>>>

We are going to run the simulations for a starting temperature of 300 kelvin,
and vary the time step from $1.0 \times 10^{-15}$ to $1.0 \times 10^{-14}$
seconds with 40 intermediate values. The results, as shown in figure
\ref{fig:energy_fluctuations}, tells us exactly how much better Velocity Verlet
is when it comes to energy conservation.

\begin{figure}[h]
    \centering \includegraphics[width=0.8\linewidth]{energy_fluctuations.pdf}
    \caption[Energy fluctuations]{The standard deviation of the total energy as
        a function of the time-step $\Delta t$ with the energy being per atom.
        This clearly shows the benefits of using Velocity-Verlet over
    Euler-Cromer. While Euler-Cromer gives rise to fluctuations that scale
somewhat linearly in the time step $\Delta t$, the fluctuations attributed to
Velocity-Verlet is negligible in comparison.}
    \label{fig:energy_fluctuations}
\end{figure}

\subsection{Initial to final temperature}
\label{sub:initial_to_final_temperature}

We are now interested in determining what initial temperature $T_i$ is needed
in order to have a final temperature of $T$.  One way of examining this is by
looking at the ratio $T/T_i$. 
\subsection{Melting temperature of system}
\label{sub:melting_temperature_of_system}
